\ttitle

### 2013-07-03 Appendices/AppendixA-summaries.tex
Work on Ch2
Rough finish of chapter 2
Adding acronym-glosarries

Please ignore this Appendix.
This appendix is for my own personal use.
It contains summaries of articles I have read.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Support Vector Machines}

@@

%--------------------------------------------
\subsubsection{Multiple changes: Iterated cumulative sums of squares}\label{subsec:icss}
In case of a single change point the $D_k$ method would succeed.
But we are interested in multiple change points of variance, and thus the usefulness of the $D_k$ reduces due to the masking effect.
A solution is to iteratively applying the method and dividing the series at each possible change point.
The algorithm is presented in table \ref{tab:icss}.
It is the third steps which reduces the masking effect and helps to ``fine tune'' the algorithm by (re)moving the potential change points by checking each location given the adjacent ones.

\begin{center}\begin{table}
\begin{tabular}{ l p{12cm} }
  \hline
  Step & Action \\
  \hline
  0 & Let $t_1 = 1$ \\
  1 & Calculate $D_k(\alpha[t_1 : T])$. Let $k^*(\alpha[t_1 : T])$ be the point at which $\text{max}_k \abs{D_k(\alpha[t_1 : T])}$. Let $D^*$ be the asymptotically critical value and $M$ the max value in the series segment (?). If $M > D^*$ then consider $k^*$ to be a change point. Else, there is no change point and the algorithm stops. \\
  2a & Repeat for the first part (up to the change point), until no more change points are found. \\
  2b & Repeat for the second part (from the change point forward), until no more change points are found. \\
  3 & When two or more change points are found; check for each $\alpha[j-1 : j+1]$ if there is indeed a change point ($j$). Repeat until the number of change points does not change and each new found change point is ``close'' enough to previous. \\
  \hline
\end{tabular}
\caption{Iterated Cumulative Sums of Squares (ICSS) Algorithm}
\label{tab:alg-svcdp}
\end{table}\end{center}

\subsubsection{Results}
When the ICSS algorithm was applied to stock data, it resulted in comparable results as the maximum likelihood estimates and Bayesian analysis.
The performance (CPU-time and correct observations with artificial data) of ICSS outperforms the other two.
The heavy computational burden of posterior odds can be partially alleviated by the maximum log-likelihood method.
The ICSS algorithm avoids calculating a function at all possible locations of change points due the iterative manner.

@@

%--------------------------------------------
\subsubsection{Introduction}
The problem of change-point detection is well studied over the last decades in the field of statistics.
A common statistical formulation of change-point detection is to consider the probability distributions over past and present data intervals, and regard the target time as a change-point if the two distributions are significantly different.
Some approaches (such as CUSUM and GLR) make use of the \emph{log-likelihood ratio}, and are extensively explored in the data mining community.
Many approaches (novelty detection, maximum-likelihood ratio, learning of autoregressive models, subspace identification) rely on pre-specified parametric models (probability density models, autoregressive models, state-space models).
That makes it less applicable to real-life problems.
There have been some non-parametric density estimation approaches proposed, but that is known to be a hard problem.
The key idea of this paper to directly estimate the \emph{ratio} of the probability densities (also known as \emph{importance}).
The Kullback-Leibler Importance Estimation Procedure (KLIEP) is an example, but it is a batch algorithm.
This paper introduces an online version of the KLIEP algorithm and develops a flexible and computationally efficient change-point detection method.
This method is equipped with a natural cross validation procedure and thus the value of tuning parameters can be objectively determined.

>>>>

\emph{Please ignore this Appendix.
This appendix is for my own personal use.
It contains summaries of articles I have read.
}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Support Vector Machines}

@@

%--------------------------------------------
\subsubsection{Multiple changes: Iterated cumulative sums of squares}\label{subsec:icss}
In case of a single change point the $D_k$ method would succeed.
But we are interested in multiple change points of variance, and thus the usefulness of the $D_k$ reduces due to the masking effect.
A solution is to iteratively applying the method and dividing the series at each possible change point.
The algorithm is presented in table \ref{tab:alg-icss}.
It is the third steps which reduces the masking effect and helps to ``fine tune'' the algorithm by (re)moving the potential change points by checking each location given the adjacent ones.

\begin{center}\begin{table}
\begin{tabular}{ l p{12cm} }
  \hline
  Step & Action \\
  \hline
  0 & Let $t_1 = 1$ \\
  1 & Calculate $D_k(\alpha[t_1 : T])$. Let $k^*(\alpha[t_1 : T])$ be the point at which $\text{max}_k \abs{D_k(\alpha[t_1 : T])}$. Let $D^*$ be the asymptotically critical value and $M$ the max value in the series segment (?). If $M > D^*$ then consider $k^*$ to be a change point. Else, there is no change point and the algorithm stops. \\
  2a & Repeat for the first part (up to the change point), until no more change points are found. \\
  2b & Repeat for the second part (from the change point forward), until no more change points are found. \\
  3 & When two or more change points are found; check for each $\alpha[j-1 : j+1]$ if there is indeed a change point ($j$). Repeat until the number of change points does not change and each new found change point is ``close'' enough to previous. \\
  \hline
\end{tabular}
\caption{Iterated Cumulative Sums of Squares Algorithm}
\label{tab:alg-icss}
\end{table}\end{center}

\subsubsection{Results}
When the \gls{icss} algorithm was applied to stock data, it resulted in comparable results as the maximum likelihood estimates and Bayesian analysis.
The performance (CPU-time and correct observations with artificial data) of \gls{icss} outperforms the other two.
The heavy computational burden of posterior odds can be partially alleviated by the maximum log-likelihood method.
The \gls{icss} algorithm avoids calculating a function at all possible locations of change points due the iterative manner.

@@

%--------------------------------------------
\subsubsection{Introduction}
The problem of change-point detection is well studied over the last decades in the field of statistics.
A common statistical formulation of change-point detection is to consider the probability distributions over past and present data intervals, and regard the target time as a change-point if the two distributions are significantly different.
Some approaches (such as \gls{cusum} and GLR) make use of the \emph{log-likelihood ratio}, and are extensively explored in the data mining community.
Many approaches (novelty detection, maximum-likelihood ratio, learning of autoregressive models, subspace identification) rely on pre-specified parametric models (probability density models, autoregressive models, state-space models).
That makes it less applicable to real-life problems.
There have been some non-parametric density estimation approaches proposed, but that is known to be a hard problem.
The key idea of this paper to directly estimate the \emph{ratio} of the probability densities (also known as \emph{importance}).
The Kullback-Leibler Importance Estimation Procedure (KLIEP) is an example, but it is a batch algorithm.
This paper introduces an online version of the KLIEP algorithm and develops a flexible and computationally efficient change-point detection method.
This method is equipped with a natural cross validation procedure and thus the value of tuning parameters can be objectively determined.

### 2013-07-03 Appendices/AppendixB-camci.tex
wip
Adding acronym-glosarries

The proposed method SVDD of Tax and Duin \cite{tax1999support, tax2004support} models the boundary of data under consideration.
Thereby it characterizes a data set and can be used to detect novel data or outliers.
The performance is compared to methods which model the distribution's density instead, using Receiver-Operating Characteristic (ROC) curves and false negative rates.
The compared methods are:
\begin{inparaenum}[\itshape (1)]
  \item normal density which estimates the mean and covariance matrix;
  \item the Parzen density where the width of the Parzen kernel is estimated;
  \item a Gaussian Mixture Model optimized using EM; and
  \item the Nearest-Neighbor Method which compares the local density of an object with the density of the nearest neighbor in the target set (and is thus, just as SVDD, a boundary-based method).
\end{inparaenum}
The results show that when the problem formulation is to characterize an area in a feature space (and not the complete density distribution) SVDD gives a good data description.

@@

Why use SVM for density estimation? Look for justification, perhaps a review paper which compares/mentions SVM for temporal segmentation of (human activity type of) data?

Why use RBF/Gaussian kernel? Is it because of one-class SVM of because of form the data? Why not polynomial/linear?
\begin{itemize}
  \item ``Use RBF when relation between class and data is non-linear''
  \item ``RBF uses less paramters (C for penalty/soft margin and gamme for kernel width) than non-linear polynomial kernels''
  \item (arguments from \cite{zhang2011optimal} ``Optimal model selection for posture recognition in home-based healthcare'')
\end{itemize}

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Relation to other methods}

\subsection{Novelty/outlier detection}
*** Read \cite{hodge2004survey} ``A survey of outlier detection methodologies'' to compare with other methodologies. ***

>>>>

The proposed method \gls{svdd} of Tax and Duin \cite{tax1999support, tax2004support} models the boundary of data under consideration.
Thereby it characterizes a data set and can be used to detect novel data or outliers.
The performance is compared to methods which model the distribution's density instead, using Receiver-Operating Characteristic (ROC) curves and false negative rates.
The compared methods are:
\begin{inparaenum}[\itshape (1)]
  \item normal density which estimates the mean and covariance matrix;
  \item the Parzen density where the width of the Parzen kernel is estimated;
  \item a Gaussian Mixture Model optimized using EM; and
  \item the Nearest-Neighbor Method which compares the local density of an object with the density of the nearest neighbor in the target set (and is thus, just as SVDD, a boundary-based method).
\end{inparaenum}
The results show that when the problem formulation is to characterize an area in a feature space (and not the complete density distribution) SVDD gives a good data description.

@@

Why use \gls{svm} for density estimation? Look for justification, perhaps a review paper which compares/mentions SVM for temporal segmentation of (human activity type of) data?

Why use RBF/Gaussian kernel? Is it because of one-class SVM of because of form the data? Why not polynomial/linear?
\begin{itemize}
  \item ``Use RBF when relation between class and data is non-linear''
  \item ``RBF uses less paramters (C for penalty/soft margin and gamme for kernel width) than non-linear polynomial kernels''
  \item (arguments from \cite{zhang2011optimal} ``Optimal model selection for posture recognition in home-based healthcare'')
  \item Survey \cite{hodge2004survey} states RBF is similair to Gaussian Mixture model (page 25).
\end{itemize}

*** TODO: read \cite{mavroforakis2006geometric} and \cite{bennett2000duality} on geometry of SVMs ***

@@

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

*** Note: in \cite{mavroforakis2006geometric} it is explained why the inner-product between two vectors is a logical choice for the distance/similarity measure. ***

\section{Relation to other methods}

\subsection{Novelty/outlier detection}
*** Read \cite{hodge2004survey} ``A survey of outlier detection methodologies'' to compare with other methodologies. ***
\begin{itemize}
  \item One-class classification is referred to as ``Type 3'', with \emph{semi-supervised recognition or detection}.
  \item It explains why one-class can be beneficial over type-2 where negative examples needs to be provided.
  \item We are interested in type-3, so compare SVM with the others stated in this survey regarding type-3.
  \item Often refers to the convex hull of the data set. Link with geometric approach as in \cite{bennett2000duality,mavroforakis2006geometric}?
  \item It states that PCA and regression techniques are linear models and thus often are too simple for practical applications. SVMs try to find a hyperplane in higher dimensional space; linear models to implement complex class boundaries. It refers to \cite{tax1999support}.
\end{itemize}

### 2013-07-03 Chapters/Chapter2.tex
Adding acronym-glosarries

\section{Statistical framework}\label{statistical-framework}
Many applications require the detection of time points at which the underlying properties of a system change.
This problem thus has received a lot of attention in the fields of data mining, etc... *** list and refs ***.
Often this problem is formulated in a statistical framework, by inspecting the data generating PDF (Probability Density Function) of the time series data.
A change point is then defined as a significant change in the properties of the PDF, such as the mean and variance.

The widely used CUSUM (cumulative sum) method by Basseville \etal \cite{basseville1993detection} takes this approach.
It originates from control methods for detection from bench marks.
This method and some derivatiges are discussed and analyzed in section \ref{cusum}.

Many methods rely on pre-specified parametric model assumptions and considers the data be independent over time, which makes it less flexible to real-world applications.
The proposed methods by Kawahara \etal \cite{kawahara2009change} and Lui \etal \cite{liu2013change} try to overcome these problems by estimating the \emph{ratio} between the PDF, instead of estimating each PDF.
This approach is discussed and analyzed in section \ref{density-ratio}.

The density-estimation methods rely on the log-likelihood ratio between PDFs.
The method of Camci \cite{camci2010change} takes an other approach within the statistical framework, by using a SVM (Support Vector Machine).
One problem it tries to overcome is the (claimed) weakness of many methods to detect a decrease in variance.
The method represents the distribution over the data points as a hyper-sphere in a higher dimension using kernel trick.
A change in the PDF is represented by a change in the radius of this sphere.
Section \ref{svm} discusses the SVM-method.

>>>>

\section{Statistical framework}\label{statistical-framework}
Many applications require the detection of time points at which the underlying properties of a system change.
This problem thus has received a lot of attention in the fields of data mining, etc... *** list and refs ***.
Often this problem is formulated in a statistical framework, by inspecting the data generating \gls{pdf} of the time series data.
A change point is then defined as a significant change in the properties of the \gls{pdf}, such as the mean and variance.

The widely used \gls{cusum} method by Basseville \etal \cite{basseville1993detection} takes this approach.
It originates from control methods for detection from bench marks.
This method and some derivatiges are discussed and analyzed in section \ref{cusum}.

Many methods rely on pre-specified parametric model assumptions and considers the data be independent over time, which makes it less flexible to real-world applications.
The proposed methods by Kawahara \etal \cite{kawahara2009change} and Lui \etal \cite{liu2013change} try to overcome these problems by estimating the \emph{ratio} between the \gls{pdf}, instead of estimating each \gls{pdf}.
This approach is discussed and analyzed in section \ref{density-ratio}.

The density-estimation methods rely on the log-likelihood ratio between \glspl{pdf}.
The method of Camci \cite{camci2010change} takes an other approach within the statistical framework, by using a \gls{svm}.
One problem it tries to overcome is the (claimed) weakness of many methods to detect a decrease in variance.
The method represents the distribution over the data points as a hyper-sphere in a higher dimension using kernel trick.
A change in the \gls{pdf} is represented by a change in the radius of this sphere.
Section \ref{svm} discusses the \gls{svm}-method.

### 2013-07-03 Chapters/Chapter2/cusum.tex
Adding acronym-glosarries

Non-Bayesian change detection algorithm (thus: no prior distribution believe available for the change time).
The CUSUM (cumulative sum) method is developed by Page \cite{page1954continuous} for the application of statistical quality control (it is also known as a control chart).
Primary for detection of mean shift.
The MOSUM of squares test for monitoring variance changes \cite{hsu2007mosum}.
Use of Cumulative Sums of Squares for Retrospective Detection of Changes of Variance \cite{inclan1994use}

An often used approach in the statistical framework of change detection is the Cumulative Sum of Squares (CUSUM) as introduced by Page \cite{page1954continuous}.
Originally used for quality control in production environments, its main function is to detect change in the mean of measurements and has been applied to this problem \cite{basseville1993detection}.
It is an non-Bayesian method and thus makes no assumptions (or: prior belief distributions) for the change points.
Many extensions to this method have been proposed.
Some focus on the change in mean, such the method of Alippi and Roveri \cite{alippi2006adaptive}.
Others apply the method the problems in which the change of variance is under consideration.
Among others are there the centered version of the cumulative sums, introduced by Brown, Durbin and Evans \cite{brown1975techniques} and the Moving Sum (MOSUM) of squares by \cite{hsu2007mosum}.

The method of Incl\'{a}n and Tiao \cite{inclan1994use} builds on the centered version of CUSUM \cite{brown1975techniques} to detect changes in variance.
Using the Iterative Cumulative Sum of Squares (ICSS) algorithm they are able to find multiple change points in a reflective manner.
Let $C_k = \sum_{i=1}^k \alpha_t^2$ be the cumulative sum of squares for a series of uncorrelated random variables $\{\alpha_t\}$ of length $T$.
The centered (and normalized) sum is squares is defined as
\begin{equation}
  \begin{aligned}
  D_k = \frac{C_k}{C_T} - \frac{k}{T}, & & k = 1, \dots, T, & & \text{with } D_0 = D_T = 0.
  \end{aligned}
\end{equation}
For a series with homogeneous variance, the value of $D_k$ will oscillate around $0$.
When there is a sudden change, the value will increase and exceed some predefined boundary with high probability.
The behavior of $D_k$ is related a Brownian bridge.
By using an iterative algorithm, the method is able to minimize the masking effect of successive change points.

One of the motivations for the ICSS algorithm was the heavy computational burden involved with Bayesian methods, which need to calculate the posterior odds for the log-likelihood ratio testing.
The ICSS algorithm avoids applying a function at all possible locations, due to the iterative search.
The authors recommend the algorithm for analysis of long sequences.

>>>>

Non-Bayesian change detection algorithm (thus: no prior distribution believe available for the change time).
The \gls{cusum} method is developed by Page \cite{page1954continuous} for the application of statistical quality control (it is also known as a control chart).
Primary for detection of mean shift.
The \gls{mosum} of squares test for monitoring variance changes \cite{hsu2007mosum}.
Use of Cumulative Sums of Squares for Retrospective Detection of Changes of Variance \cite{inclan1994use}

An often used approach in the statistical framework of change detection is the \gls{cusum} as introduced by Page \cite{page1954continuous}.
Originally used for quality control in production environments, its main function is to detect change in the mean of measurements and has been applied to this problem \cite{basseville1993detection}.
It is an non-Bayesian method and thus makes no assumptions (or: prior belief distributions) for the change points.
Many extensions to this method have been proposed.
Some focus on the change in mean, such the method of Alippi and Roveri \cite{alippi2006adaptive}.
Others apply the method the problems in which the change of variance is under consideration.
Among others are there the centered version of the cumulative sums, introduced by Brown, Durbin and Evans \cite{brown1975techniques} and the \gls{mosum} of squares by \cite{hsu2007mosum}.

The method of Incl\'{a}n and Tiao \cite{inclan1994use} builds on the centered version of \gls{cusum} \cite{brown1975techniques} to detect changes in variance.
Using the \gls{icss} algorithm they are able to find multiple change points in a reflective manner.
Let $C_k = \sum_{i=1}^k \alpha_t^2$ be the cumulative sum of squares for a series of uncorrelated random variables $\{\alpha_t\}$ of length $T$.
The centered (and normalized) sum is squares is defined as
\begin{equation}
  \begin{aligned}
  D_k = \frac{C_k}{C_T} - \frac{k}{T}, & & k = 1, \dots, T, & & \text{with } D_0 = D_T = 0.
  \end{aligned}
\end{equation}
For a series with homogeneous variance, the value of $D_k$ will oscillate around $0$.
When there is a sudden change, the value will increase and exceed some predefined boundary with high probability.
The behavior of $D_k$ is related a Brownian bridge.
By using an iterative algorithm, the method is able to minimize the masking effect of successive change points.

One of the motivations for the \gls{icss} algorithm was the heavy computational burden involved with Bayesian methods, which need to calculate the posterior odds for the log-likelihood ratio testing.
The \gls{icss} algorithm avoids applying a function at all possible locations, due to the iterative search.
The authors recommend the algorithm for analysis of long sequences.

### 2013-07-03 main.tex
More on HMM
Add marco for et al. abbrevation
Starting summary Peter Flach
Add double bar notations
Use `\norm` for double bar notions, following
http://tex.stackexchange.com/questions/43008/absolute-value-symbols/43009#43009
Add `argmin` and `argmax` defs.
Putting Camci-flaws in text
Adding acronym-glosarries

\usepackage[square, numbers, comma, sort&compress]{natbib} % Use the natbib 
%reference package - read up on this to edit the reference style; if you want 
%text (e.g. Smith et al., 2012) for the in-text references (instead of 
%numbers), remove 'numbers' 
\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue - 
%change to black if annoying
\title{\ttitle} % Defines the thesis title - don't touch this

\begin{document}

@@

@@

%----------------------------------------------------------------------------------------
%	ABBREVIATIONS
%----------------------------------------------------------------------------------------

\setstretch{1.5} % Set the line spacing to 1.5, this makes the following tables easier to read

\lhead{\emph{Abbreviations}} % Set the left side page header to "Abbreviations"
\listofsymbols{ll} % Include a list of Abbreviations (a table of two columns)
{
\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere \\
%\textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
}

%----------------------------------------------------------------------------------------
%	PHYSICAL CONSTANTS/OTHER DEFINITIONS
%----------------------------------------------------------------------------------------

\lhead{\emph{Physical Constants}} % Set the left side page header to "Physical Constants"

\listofconstants{lrcl} % Include a list of Physical Constants (a four column table)
{
Speed of Light & $c$ & $=$ & $2.997\ 924\ 58\times10^{8}\ \mbox{ms}^{-\mbox{s}}$ (exact)\\
% Constant Name & Symbol & = & Constant Value (with units) \\
}

@@

\setstretch{1.3} % Return the line spacing back to 1.3

@@

\input{./Chapters/Chapter1}
\input{./Chapters/Chapter2} 
\input{./Chapters/Chapter3}
\input{./Chapters/Chapter4} 
\input{./Chapters/Chapter5} 
\input{./Chapters/Chapter6} 
%\input{./Chapters/Chapter7}

@@

\input{./Appendices/AppendixA}
%\input{./Appendices/AppendixB}
%\input{./Appendices/AppendixC}

>>>>

\usepackage[square, numbers, comma, sort&compress]{natbib} % Use the natbib
%reference package - read up on this to edit the reference style; if you want
%text (e.g. Smith et al., 2012) for the in-text references (instead of
%numbers), remove 'numbers'
\usepackage{isomath}
\usepackage{paralist}
\hypersetup{urlcolor=blue, colorlinks=true} % Colors hyperlinks in blue -
%change to black if annoying
\title{\ttitle} % Defines the thesis title - don't touch this

% Use double bar notations: http://tex.stackexchange.com/questions/43008/absolute-value-symbols/43009#43009
\usepackage{mathtools}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%

% Swap the definition of \abs* and \norm*, so that \abs
% and \norm resizes the size of the brackets, and the
% starred version does not.
\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
%
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\makeatother
% End of double bar notations

\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}

% \usepackage{hyperref}
\usepackage[nomain,acronym,xindy,toc]{glossaries}
\renewcommand*{\glstextformat}[1]{\textcolor{black}{#1}}
\makeglossaries
\usepackage[xindy]{imakeidx}
\makeindex

\begin{document}
\include{glossary-acronyms}
\include{glossaries}

@@

\ExplSyntaxOn
\newcommand\latinabbrev[1]{
  \peek_meaning:NTF . {% Same as \@ifnextchar
    #1\@}%
  { \peek_catcode:NTF a {% Check whether next char has same catcode as \'a, i.e., is a letter
      #1.\@\ }%
    {#1.\@\ }}}
\ExplSyntaxOff

%Omit final dot from each def.
\def\eg{\latinabbrev{e.g}}
\def\etal{\latinabbrev{\textit{et al}}}
\def\etc{\latinabbrev{etc}}
\def\ie{\latinabbrev{i.e}}

@@

% %----------------------------------------------------------------------------------------
% %	ABBREVIATIONS
% %----------------------------------------------------------------------------------------

% \clearpage % Start a new page

% \setstretch{1.5} % Set the line spacing to 1.5, this makes the following tables easier to read

% \lhead{\emph{Abbreviations}} % Set the left side page header to "Abbreviations"
% \listofsymbols{ll} % Include a list of Abbreviations (a table of two columns)
% {
% \textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere \\
% %\textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
% \textbf{PCA} & \textbf{P}rinciple \textbf{C}omponent \textbf{A}nalysis
% }

%----------------------------------------------------------------------------------------
% GLOSSARIES
%----------------------------------------------------------------------------------------

\clearpage

\lhead{\emph{Acronyms}}

\printglossaries

% %----------------------------------------------------------------------------------------
% %	PHYSICAL CONSTANTS/OTHER DEFINITIONS
% %----------------------------------------------------------------------------------------

% \clearpage % Start a new page

% \lhead{\emph{Physical Constants}} % Set the left side page header to "Physical Constants"

% \listofconstants{lrcl} % Include a list of Physical Constants (a four column table)
% {
% Speed of Light & $c$ & $=$ & $2.997\ 924\ 58\times10^{8}\ \mbox{ms}^{-\mbox{s}}$ (exact)\\
% % Constant Name & Symbol & = & Constant Value (with units) \\
% }

@@

\clearpage
\setstretch{1.3} % Return the line spacing back to 1.3

@@

\input{./Chapters/Chapter1}
\input{./Chapters/Chapter2}
\input{./Chapters/Chapter3}
\input{./Chapters/Chapter4}
\input{./Chapters/Chapter5}
\input{./Chapters/Chapter6}
\input{./Chapters/Chapter7}

@@

\input{./Appendices/AppendixA-Summaries}
\input{./Appendices/AppendixB-Camci}
%\input{./Appendices/AppendixB}
%\input{./Appendices/AppendixC}
